\pagenumbering{roman}
% 		\large
% 			\chapter*{BONAFIDE CERTIFICATE}
% 		\normalsize 
% 		\addcontentsline{toc}{section}{BONAFIDE CERTIFICATE}

% 	 This is to certify that the project entitled \textbf{“Voice Assistant for Visually Impaired People”} submitted by \textbf{ Avyudaya Karn (590301), Birendra Chawal (590307), Rohit Kumar Mahato (590316) and  Sunil Chikanbanjar (590336)} in partial fulfillment of the requirements for the award of the degree of \textbf{Bachelor of Engineering in Computer Engineering} of Purbanchal University, is a bonafide work to the best of our knowledge and may be placed before the examination board for their consideration.\\ 

%  \vspace{1 cm}

% \underline{\textbf{Panel Of Examiners:}}
% \qquad\qquad\qquad\qquad\qquad\qquad\qquad\qquad\underline{\textbf{Signature}}

% \vspace{1cm}

% \textbf{1. External Examiner} \\
% Person 1 Name \\
% Designation \\
% Institute/University Name \\
% Date\\

% \vspace{1cm}

% \textbf{2. Supervisor} \\
%  Person 2 Name  \\
%  Designation  \\
%  Institute/University Name  \\
%  Date \\

% \textbf{3. Head of Department} \\
% Person 3 Name \\
% HoD \\
% Khwopa Engineering College \\
% Date\\

% \vspace{1cm}





% 		\large
% 		\chapter*{Copyright}
% 		\normalsize
% 		\addcontentsline{toc}{section}{Copyright}
% 			The author has agreed that the library, Khwopa   Engineering College  may make this report freely available for inspection. Moreover, the author has agreed that permission for the extensive copying of this project report for scholarly purpose may be granted by supervisor who supervised the project work recorded here in or, in absence the Head of the Department where in the project report was done. It is understood that the recognition will be given to the author of the report and to Department of Computer Engineering, KhEC in any use of the material of this project report. Copying or publication or other use of this report for financial gain without approval of the department and author’s written permission is prohibited. Request for the permission to copy or to make any other use of material in this report in whole or in part should be addressed to: \\
% 			\vspace{1cm} \\
% 			Head of Department \\
% 			Department of Computer Engineering\\
% 			Khwopa Engineering College\\
% 			Libali-08,\\
% 			Bhaktapur, Nepal\\
% 		\pagebreak


\large
\chapter*{Acknowledgement}
\normalsize
\addcontentsline{toc}{section}{Acknowledgement}
We take this opportunity to express our deepest and sincere gratitude for the chance to work on our project, \textbf{'Predictive Site Selection System'}. This work is submitted as a partial fulfillment of the requirements for the seventh semester of our Bachelor of Computer Engineering degree under Purbanchal University.

\noindent
We are sincerely thankful to our institution, \textbf{Khwopa Engineering College}, for providing us with the platform and resources necessary to undertake this project. We would like to extend our special and heartfelt gratitude to our Head of the Department of Computer Engineering, \textbf{Er. Bikash Chawal}, for his invaluable guidance and for providing us with this golden opportunity to apply our skills to a real-world challenge.

\noindent
This project is not just an academic exercise; it is our endeavor to bridge the gap between complex data science and practical, everyday business decisions. We would also like to express our sincere gratitude to all those whose ideas, insights, and innovations have inspired this project.
\begin{table}[h]
	\begin{tabular}{ll}
		Anish Maka      & (780304) \\
		Roj Gosai    & (780334) \\
		Subekshya Kadel & (780341) \\
		Sujal Koju & (780342)
	\end{tabular}
\end{table}
\pagebreak

\large
\chapter*{Abstract}
\normalsize
\addcontentsline{toc}{section}{Abstract}
Selecting an optimal location is a critical, high-risk decision for new entrepreneurs, who often rely on intuition and incomplete data, leading to high business failure rates. This project presents a comprehensive Location Intelligence and Decision Support Platform, designed to address this challenge by providing data-driven, personalized site selection analysis for small and medium-sized businesses in Nepal.

The proposed system moves beyond generic success prediction by first capturing the user's unique business profile, including their specific strategy (e.g., 'Quiet Study Hub' vs. 'Tourist Hotspot'), budget, and property requirements. It leverages a multi-layered geospatial database of competitor locations, points of interest, and derived neighborhood-level demographic proxies. By integrating a machine learning model (XGBoost), the platform generates a personalized 'Opportunity Zone' heatmap and calculates a tailored 'Suitability Score' for any chosen location.

Crucially, the system provides an explainable AI-driven breakdown of the score, along with a suite of analytical tools: dynamic trade area analysis (isochrones), detailed competitor insights, and an integrated real estate discovery feature that shows available 'To-Let' properties. The result is an end-to-end platform that bridges the gap between analysis and action, empowering entrepreneurs to make evidence-based decisions. It democratizes access to sophisticated data science, significantly reducing the risks associated with starting a new business.\\\\
\textbf{Keywords}: \textit{Location Intelligence, Geospatial Analysis, Predictive Analytics, Decision Support System, Site Selection, Explainable AI}

\pagebreak