\chapter{Conclusion and Enhancements}
\section*{Conclusion}

In conclusion, SiteX has been successfully developed as a Location Intelligence and Site-Suitability application tailored specifically for cafe and restaurant businesses. The system enables entrepreneurs to evaluate potential locations by selecting a point on the map and receiving a suitability score along with an associated risk level. 

By analyzing surrounding commercial activity, competitor presence, and neighborhood characteristics, the platform transforms complex spatial information into clear and actionable insights. SiteX bridges the gap between raw geospatial data and real-world business decisions, helping reduce uncertainty and financial risk when launching or expanding a food-service business in Nepal.

\section*{Future Enhancements}

While the current system provides a strong foundation for data-driven site evaluation, several enhancements can further improve its accuracy, usability, and scalability:

    \begin{itemize}

            \item \textbf{Personalized Business Input:} Allow users to define their café or restaurant profile, including business type (e.g., franchise café, quick-service restaurant), target customer segment, budget constraints, and space requirements to generate more customized suitability assessments.
            \item \textbf{Real-Time Data Integration:} Incorporate real-time foot traffic and mobility data from sources like mobile location services or social media check-ins to provide dynamic, up-to-date location assessments.
            \item \textbf{Expanded Economic Indicators:} Integrate additional economic data such as rental price trends, local income levels, and purchasing power analysis to enhance the predictive model's understanding of location viability.
            \item \textbf{Multi-Branch Optimization:} Develop features that allow franchise owners to plan and optimize multiple outlet locations simultaneously, considering factors like cannibalization and network effects.
            \item \textbf{Explainable AI Enhancements:} Implement more advanced explainable AI techniques to provide users with deeper insights into the reasoning behind suitability scores, including visualizations of feature importance and scenario analysis.
            \item \textbf{Support for Additional Food-Service Categories:} Expand the system to support other types of food-service businesses such as fine dining restaurants, fast-food chains, and cloud kitchens, each with tailored analysis criteria.
            \item \textbf{Café Categorization and Characterization:} Develop a robust classification framework that categorizes cafés and restaurants based on attributes such as ambiance, cuisine type, price range, seating capacity, and target demographic. By characterizing each business type in detail, the system can deliver more context-aware suitability assessments tailored to the specific nature of the establishment.
            \item \textbf{Prescriptive Location Recommendations:} Move beyond evaluating a single user-selected point to actively prescribing optimal locations based on the type of café or restaurant the user intends to open. By combining the categorization framework with spatial analysis, the system can suggest the best-suited areas, neighborhoods, or streets for a given business profile, enabling truly prescriptive decision-making.
            \item \textbf{Advanced Deep Learning Models:} Transition from the current XGBoost-based approach to more sophisticated deep learning architectures such as deep neural networks, graph neural networks, or transformer-based spatial models. While XGBoost provides a solid and interpretable baseline, deep learning models can capture more complex, non-linear relationships among spatial, economic, and demographic features, potentially yielding higher predictive accuracy and better generalization across diverse urban landscapes.
    \end{itemize}