\chapter{PROJECT WORK STATUS}\label{chap:outcomes}
\section{Completed Works}

Upon completion, this project will deliver more than an academic exercise; it will be a functional, professional-grade Predictive Site Selection System named \textbf{SiteX}. Our primary goal is to create a live web application that serves as an indispensable strategic partner for business owners. We envision a friend, a \textit{dai} or \textit{didi}, using SiteX not just to find a "good" location, but to discover the \textit{right} location that aligns perfectly with their unique business vision, budget, and strategy, thereby transforming a high-stakes gamble into a data-informed decision.

\vspace{0.4cm}
\noindent
The final application will not merely provide a single, static "success score." Instead, it will offer a comprehensive and interactive decision-support dashboard tailored to the user's specific needs. We expect the user to be able to:
\begin{itemize}
    \item Define their unique business profile.
    \item Explore a dynamic heatmap that visualizes opportunity zones personalized to their specific profile.
    \item Seamlessly discover and analyze available "To-Let" properties directly on the map.
    \item Receive a \textbf{Personalized Suitability Score} for any selected point, accompanied by an explainable AI breakdown that clearly articulates the \textit{why}  the positive and negative drivers behind the score.
    \item Conduct in-depth competitor analysis, visualize a realistic customer trade area using isochrones, and understand the neighborhood's demographic alignment with their target audience.
    \item Generate a one-click, professional PDF report summarizing the entire analysis for business planning and investor pitches.
\end{itemize}
In essence, we are leveling the playing field, providing the kind of sophisticated, data-driven insights previously accessible only to large corporations, and making them intuitive for local entrepreneurs.

\vspace{0.4cm}
\noindent
On a personal and technical level, this project represents the culmination of our entire engineering education. It is our opportunity to synthesize theory from multiple domains geospatial analysis with PostGIS and QGIS, high-performance backend development with FastAPI, modern frontend design with React, and advanced machine learning with XGBoost. We are not just training a model; we are architecting and building a complete, end-to-end data science solution from scratch. We expect to emerge from this project not just as students who completed a requirement, but as engineers who have designed, built, and deployed a robust, data-intensive application that solves a tangible, meaningful problem for our own community here in Nepal.